How do galaxies get assigned to halos? \\ Searching for assembly bias in the SDSS galaxy clustering

### 2016-09-28 text/ms.tex
the most updated version of the text

Most theories of cosmology and large-scale structure formation under consideration today rely on the central assumption that galaxies reside in dark-matter halos. Detailed study of the galaxy--halo connection is therefore critical in order to constrain cosmological models (by modeling galaxy clustering at non-linear scales) as well as providing a window into galaxy formation physics. One of the most powerful methods for describing the galaxy-halo connection is the halo occupation 
distribution (HOD, see \citealt{seljak2000, berlind_weinberg2002, scoccimarro2001, zheng2005, zheng07, leauthaud12, tinker2013, decorated, 2016arXiv160701782H}).

@@

Despite this very simplifying assumption, the models of galaxy-halo connection based on HOD modeling have been very successfully used in fitting the measurements of a wide range of statistics such as the projected two-point correlation function of galaxies, small scale redshift space distortion, three-point function, and galaxy--galaxy lensing with remarkable success (e.g. \citealt{zheng07,tinker_rsd2007,zehavi2011,leauthaud12,parejko2013,coupon2015,hod-3pcf,guo2015,miyatake15,zu2015,hod_vs_sham}). 
HOD has been used in constraining the cosmological parameters through modeling the galaxy two-point correlation function (hereafter 2PCF) (\citealt{abazajian2005}), combination of 2PCF with mass-to-light ratio of galaxies (\citealt{tinker05}), redshift space distortions (\citealt{tinker_rsd2007}), mass-to-number ratio of galaxy clusters (\citealt{tinker2012}) galaxy-galaxy weak lensing (\citealt{vdb03,cacciato13,more13,vdb13}) in the main sample of galaxies
of the Sloan Digital Sky Survey (hereafter SDSS, \citealt{york2000}), and also the combination of galaxy clustering and galaxy-galaxy lensing (\citealt{more15}) in SDSS III Baryon Oscillation Spectroscopic Survey (BOSS, \citealt{boss}). Furthermore, HOD is implemented in producing mock galaxy catalogs in the BOSS survey (\citealt{manera2013,white2014}). It has also been used in galaxy evolution studies (\citealt{conroy09,leauthaud12,behroozi13,hudson2015,zu2015,zu2016}).

@@

Another family of empirical galaxy-halo connection models is \emph{Abundance} \emph{Matching}. In Abundance Matching models, galaxies are assumed to live in halos/subhalos and are assigned luminosities or stellar masses by assuming a one-to-one mapping that preserves the rank ordering between its host halo/subhalo property and its luminosity or stellar mass
(\citealt{kravtsov2004,vale2004,tasitsiomi2004,conroy2009,guo2010,wetzel2010,Neisten2011,watson2012,rodriguez2012,kravstov2013,mao2015,chavez2016}). 
In practice, the standard abundance-matching models assume a monotonic mapping between the stellar mass/luminosity of galaxies and some host-halo property, such as 
the maximum circular velocity the host halo $V_\mathrm{max}$ that traces the depth of the gravitational potential well of the halo. Furthermore, a scatter is assumed in this one-to-one relation between galaxy property and halo/subhalo property. With this framework, abundance-matching models have been successfully used in modeling a wide range of the 
statistical properties of galaxies such as two-point correlation function (\citealt{reddick2013,lehman2015,hod_vs_sham}) as well as the group statistics of galaxies (\citealt{sham_gmf}).

@@

In the $\mathtt{SMDP}$ simulation, as discussed in \citealt{halodemographic}, the Rockstar algorithm can reliably resolve halos with $\geq 100$ particles which corresponds to $M_{\rm vir} \geq 9.6 \times 10^{9} \; h^{-1}M_{\odot}$. The advantage of using the $\mathtt{SMDP}$ simulation is that it satisfies both the size and resolution requirements of studying the galaxy-halo connection. Fainter galaxy samples reside in lower mass halos, and the more luminous galaxy samples considered in this investigation occupy higher comoving volumes. Furthermore, since we are studying the higher order halo occupation statistics, the concentration-dependence in particular, it is important to use a simulation that can resolve the internal structure of halos. In the context of Subhalo-Abundance matching modeling---whose accuracy hinges upon subhalo completeness especially in the low mass limit---of the galaxy-halo connection in the SDSS data, $\mathtt{SMDP}$ has been previously used to model the faint galaxy samples with absolute luminosity in the r-band $M_{\rm r}$ less -18, -18.5, and -19 (see \citealt{hod_vs_sham}). The added advantage of using the $\mathtt{SMDP}$ simulation over some industrial simulation boxes commonly used in the literature such as $\mathtt{Bolshoi}$ (\citealt{Klypin2011,smallmultidark}) simulation is its comoving volume which makes it more suitable for performing inference with $L_{\star}$ (corresponding to $M_{\rm r} \sim -20.44$, see \citealt{blanton2003}) and more luminous than $L_{\star}$ galaxy samples.

@@

For our standard HOD model, we assume the HOD parameterization from \citealt{zheng07}. 
According to this model, a dark matter halo can host a central galaxy and some number of satellite galaxies. The occupation of the central galaxies follows a nearest-integer distribution, 
and the occupation of the satellite galaxies follows a Poisson distribution. The expected number of centrals and satellites as a function of the host halo mass of $M_{\rm h}$ are given by the following equations 
\begin{eqnarray}
\langle N_{\rm cen}(M_{\rm h}) \rangle &=& \frac{1}{2}\Big[1+\Big(\frac{\log M_{\rm h} - \log M_{\rm min}}{\sigma_{\log \rm{M}}} \Big) \Big], \label{hod:central}\\ 
\langle N_{\rm sat}(M_{\rm h}) \rangle &=& \Big( \frac{M_{\rm h} - M_{\rm{0}}}{M_{\rm 1}} \Big)^{\alpha}. \label{hod:satellite}
\end{eqnarray}

For populating the halos with galaxies, we follow the procedure described in \citealt{2016arXiv160701782H,decorated}. The central galaxies are assumed to be at the center of the host dark matter halos. We assume that the central galaxies are at rest with respect to the bulk motion of the halos and their velocities are given by the velocity of the center of mass of their host halo. Note that this assumption is shown to be violated in brighter than $L_{\star}$ galaxies (see \citealt{guo2015}). But since we are not considering the redshift space 2PCF multipoles in our study, we do not expect this velocity bias to impact our inference. We place the satellite galaxies within the virial radius of the halo following a Navarro-Frenk-White profile (hereafter NFW; \citealt{nfw}). This approach is different from other simulation-based halo occupation modeling techniques (see \citealt{hod_vs_sham,zheng_guo}) in that the positions of the satellites are not assigned to the dark matter particles in the $N$-body simulation. 
The concentration of the NFW profile is given by the empirical mass-concentration relation provided by (\citealt{nfw_c(M)}). The velocities of the satellite galaxies are given by two components. The first component is the velocity of the host halo. The second component is the velocity of the satellite galaxy with respect to the host halo which is computed following the solution to the NFW profile Jeans equations (\citealt{more2010}). We refer the readers to \citealt{decorated} for a more comprehensive and detailed discussion of the forward modeling of the galaxy mock catalogs.

\subsubsection{Model with Assembly bias}\label{subsubsec:decorated}
Now let us provide a brief overview of HOD modeling with $\mathtt{Heaviside}$ $\mathtt{Assemblybias}$ (known as the decorated HOD) introduced in \citealt{decorated}. At a fixed halo mass $M_{h}$, halos are split into two populations: population of halos with the 0.5-percentile of highest concentration, and population of halos with 0.5 percentile of lowest concentration. For simplicity, we call the first population ``type-1'' halos, and the second population ``type-2'' halos. In the decorated HOD model, the expected number of central and satellite galaxies in the two populations are given by

@@

In this occupation model, the allowable range that quantities $\delta N_{c,i}$ and $\delta N_{s,i}$ can take is given by 
\begin{eqnarray}
-\langle N_{c} | M_{h}\rangle \leq \delta N_{c,i} \leq \langle N_{c} | M_{h}\rangle
 , \label{eq:cen-bounds} \\
-\langle N_{s} | M_{h}\rangle \leq \delta N_{s,i} \leq \langle N_{s} | M_{h}\rangle. \label{eq:sat-bounds}
\end{eqnarray}
Afterwards, the assembly bias parameter $\mathcal{A}$ is defined in the following way:

\begin{eqnarray}
\delta N_{\alpha , 1}(M_{h}) &=& |\mathcal{A_\alpha}| \delta N_{\alpha , 1}^{\rm max}(M_{h}) \; \; \rm{if} \; \mathcal{A_\alpha} > 0,  \label{positive_A} \\
\delta N_{\alpha , 1}(M_{h}) &=& |\mathcal{A_\alpha}| \delta N_{\alpha , 1}^{\rm min}(M_{h}) \; \; \rm{if} \; \mathcal{A_\alpha} < 0, \label{negative_A}
\end{eqnarray}
where the subscript $\alpha = c , s$ for the centrals and satellites respectively, and $\delta N_{\alpha , 1}^{\rm max}(M_{h})$, $\delta N_{\alpha , 1}^{\rm min}(M_{h})$ are given by Eqs. \ref{eq:cen-bounds} and \ref{eq:sat-bounds}.

@@

Once the halo catalogs are populated with galaxies, the real-space positions and velocities of all mock galaxies are obtained. The next step is applying a redshift-space distortion transformation by assuming plane-parallel approximation.
Our use of plane parallel approximation is justified because of the shallow depth of the SDSS main galaxy sample considered in this study.
If we assume that the $\hat{z}$ axis is the line-of-sight direction, then with the transformation $(X,Y,Z) \rightarrow (S_x,S_y,S_z) = (X , Y ,Z + v_{z}(1+z)/H(z))$
for each galaxy with the real space coordinates $(X,Y,Z)$, velocities $(v_x,v_y,v_z)$, and redshift $z$, we obtain the redshift-space coordinate of the produced mock galaxies. Here we assume $z \simeq 0$, and therefore transformation is given by $(X,Y,Z) \rightarrow (X,Y,Z+v_{z}/H_{0})$.

@@

As described in \citealt{decorated} and \citealt{2016arXiv160701782H}, this approach makes no appeal to the fitting functions used in the analytical calculation of the 2PCF. The accuracy of these fitting functions is limited (\citealt{tinker08,tinker10,watson13}). Our approach also does not face the known issues of the treatment of halo exclusion and scale-dependent bias that can lead to significant inaccuracies in halo occupation modeling (see \citealt{vdb13}).

The projected 2PCF $w_{p}(r_{p})$ can be computed by integrating the 3D redshift space 2PCF $\xi(r_{p} , \pi)$ along the line-of-sight (where $r_{\rm p}$ and $\pi$ denote the projected and line-of-sight separation of galaxy pairs respectively):
\beq
w_{p}(r_{p}) = 2 \int_{0}^{\pi_{max}}\xi(r_{p} , \pi)\; d\pi
\label{los}
\eeq
For our 2PCF calculations, we use the $w_{\rm p}$ measurement functionality of the fast and publicly available pair-counter code $\mathtt{CorrFunc}$ (\citealt{corrfunc} , available at \url{https://github.com/manodeep/Corrfunc}). To be consistent with the SDSS measurements described in \ref{sec:data}, $w_{\rm{p}}(r_{\rm{p}})$ is obtained by the line-of-sight integration to $\pi_{max}=40 \; h^{-1}\rm{Mpc}$. Note that $w_{p}(r_{p})$ is measured in units of $h^{-1}\rm{Mpc}$. To be consistent with \citealt{guo2015}, we use the same binning (as specified in Section \ref{sec:data}) to measure $w_{\rm p}$. In addition to the projected 2PCF, we use the number density given by the number of mock galaxies divided by the comoving volume of the $\mathtt{SMDP}$ simulation.

@@

The measurements consist of the number density $n_{g}$ and the projected 2PCF $w_{p}(r_{p})$ made by \citealt{guo2015} for volume-limited sample of galaxies in NYU value added galaxy catalog (\citealt{Blanton2005}) constructed from the SDSS DR7 main galaxy sample (\citealt{abazajian2009}). In particular, eight volume limited luminosity-threshold samples are constructed with maximum absolute luminosity in $r$-band ($M_{\rm r,max}$) of -18, 18.5, -19, -19.5, -20, -20.5, -21, and -21.5. Qualitatively, these samples are constructed in a similar way to those constructed in \citealt{zehavi2011}. For detailed differences between the samples in \citealt{guo2015} and \citealt{zehavi2011}, we refer the reader to the Table 1 and Table 2 in these two papers respectively.

The projected 2PCFs are measured in 12 logarithmic $r_{\rm p}$ bins (in units of $h^{-1}\rm{Mpc}$) of width $\Delta \log(r_{\rm p}) = 0.2$, starting from $r_{\rm{p}} = 0.1 \; h^{-1}\rm{Mpc}$. For all luminosity threshold samples, the integration along the line-of-sight (\ref{los}) are performed to $\pi_{max}=40 \; h^{-1}\rm{Mpc}$.

The 2PCF measurement of each luminosity threshold sample is accompanied by a covariance matrix constructed using 400 jackknife sub-samples of the data. The number density measurements are also accompanied by uncertainties measured using the jackknife method. Furthermore, the covariance between the number denisty and the projected 2PCF measurements are neglected. As \citealt{norberg} shows, parameter estimation using jackknife covariance matrices is conservative as jackknife overestimate the error in the observations.

The advantage of using these measurements is that the effects of fiber collision systematic errors on the two-point statistics are corrected for (with the method described in \citealt{guo2012}), and therefore, these measurements provide more accurate small scale clustering measurements. The assembly bias parameters introduced in section \ref{sec:method} can have a 10-percent level impacts on galaxy clustering (\citealt{decorated}). Presence of assembly bias in the satellite population impacts the very small-scale clustering (\citealt{decorated}). Moreover as \citealt{sunayama2016} demonstrates, the scale-dependence of the halo assembly bias has a pronounced bump in the 1-halo to 2-halo transition regime (1$\sim$2 $h^{-1}\rm{Mpc}$). This scales can be impacted by fiber collision systematics. Precise investigation of the possible impact of this signal on the galaxy clustering modeling requires accurate measurements of 2PCF on small scales. 
The method of \citealt{guo2012} is able to recover the true $\wpp$ with  $\sim 6\%$ accuracy in small scales ($r_{\rm{p}} = 0.1 \; h^{-1}\rm{Mpc}$) and with $\sim 2.5\%$ at relatively large scales $r_{\rm{p}} \sim 30 \; h^{-1}\rm{Mpc}$.

Note that the comoving volume of the $N$-body simulation used in this investigation is 64 $\times 10^{6} \; h^{-3}\rm{Mpc}^{3}$ which is larger than the comoving volume of all the luminosity threshold samples in the SDSS data except the two most luminous samples. The comoving volumes of the $M_{\rm r}<-21, \; 21.5$ samples are 71.74 and 134.65 (in units of $10^{6} h^{-3}\rm{Mpc}^{3}$) respectively. Since we are only studying not very large scale clustering ($r_{\rm p} \leq 25 \; h^{-1}\rm{Mpc}$), using a slightly smaller box for those samples is justified.

@@

In particular, findings of (\citealt{weschler2006,sunayama2016})
have demonstrated that for the halos with mass bellow the collapse mass ($M \leq M_{\rm col} \simeq 10^{12.5}\; M_{\odot} $) the large scale bias of high-$V_{\rm max}$ or high-$c$ halos is larger than that of the low-$V_{\rm max}$ or low-$c$ halos. This signal reverses and weakens for the high mass halos ($M \geq M_{\rm col}$). Note that the halo concentration traces the maximum circular velocity $V_{\rm max}$ such that halos with higher $V_{max}$ have higher concentration and vice versa (see \citealt{prada2012}).

@@

The luminosity dependent trend in the constraints on the central assembly bias for the six dimmest samples can be attributed to the fact that the halo concentration is highly correlated with the maximum circular velocity $V_{\rm max}$ (\citealt{prada2012}). In a dark matter halo described by an NFW profile, the depth of the gravitational potential well of dark matter halos can be directly measured by the maximum circular velocity $V_{\rm max}$ (\citealt{vmax_potential}). In particular, the magnitude of the potential well at the center of an NFW halo---where the central galaxy is assumed to reside---scales as $V_{\rm max}^{2}$. Note that this is also the quantity often used in the abundance matching technique in which the luminosity of galaxies is monotonically matched to $V_{\rm max}$ (see for example \citealt{reddick2013, hod_vs_sham, halodemographic}). The trend between the constraint on $\acen$ and the luminosity threshold of the samples may suggest that at a \emph{fixed} \emph{halo} \emph{mass}, the central galaxies in the dimmest sample ($M_{\rm r}<$-18 , -18.5) tend to reside in dark matter halos with shallower gravitational well, and as we probe brighter galaxy samples ($M_{\rm max}<$-19 , -19.5, -20, -20.5), at a \emph{fixed} \emph{halo} \emph{mass}, the central galaxies have a tendency to reside in dark matter halos with deeper gravitational potential well.

@@

However, our results suggest that for all the 8 luminosity-threshold samples, the satellite assembly bias parameter is largely unconstrained and consistent with zero. we do not expect the galaxy clustering data to be a sufficient statistics for obtaining constraints on the satellite assembly bias. Group statistics probes the high mass end of the galaxy-halo connection and is sensitive to the parameters governing the satellite population (see \citealt{sham_gmf, 2016arXiv160701782H}), and therefore these measurements may shed light on investigating assembly bias in the satellite population.

>>>>

Most theories of cosmology and large-scale structure formation under consideration today rely on the central assumption that galaxies reside in dark-matter halos. Detailed study of the galaxy--halo connection is therefore critical in order to constrain cosmological models (by modeling galaxy clustering at non-linear scales) as well as providing a window into galaxy formation physics. One of the most powerful methods for describing the galaxy--halo connection is the halo occupation 
distribution (HOD, see \citealt{seljak2000, berlind_weinberg2002, scoccimarro2001, zheng2005, zheng07, leauthaud12, tinker2013, decorated, 2016arXiv160701782H}).

@@

Despite this very simplifying assumption, the models of galaxy--halo connection based on HOD modeling have been very successfully used in fitting the measurements of a wide range of statistics such as the projected two-point correlation function of galaxies, small scale redshift space distortion, three-point function, and galaxy--galaxy lensing with remarkable success (e.g. \citealt{zheng07,tinker_rsd2007,zehavi2011,leauthaud12,parejko2013,coupon2015,hod-3pcf,guo2015,miyatake15,zu2015,hod_vs_sham}). 
HOD has been used in constraining the cosmological parameters through modeling the galaxy two-point correlation function (hereafter 2PCF) (\citealt{abazajian2005}), combination of 2PCF with mass-to-light ratio of galaxies (\citealt{tinker05}), redshift space distortions (\citealt{tinker_rsd2007}), mass-to-number ratio of galaxy clusters (\citealt{tinker2012}) galaxy-galaxy weak lensing (\citealt{vdb03,cacciato13,more13,vdb13}) in the main sample of galaxies
of the Sloan Digital Sky Survey (hereafter SDSS, \citealt{york2000}), and also the combination of galaxy clustering and galaxy-galaxy lensing (\citealt{more15}) in SDSS III Baryon Oscillation Spectroscopic Survey (BOSS, \citealt{boss}). Furthermore, HOD is implemented in producing mock galaxy catalogs in the BOSS survey (\citealt{manera2013,white2014}). It has also been used in galaxy evolution studies (\citealt{conroy09,leauthaud12,behroozi13,hudson2015,zu2015,zu2016}).

@@

Another family of empirical galaxy--halo connection models is \emph{Abundance} \emph{Matching}. In Abundance Matching models, galaxies are assumed to live in halos/subhalos and are assigned luminosities or stellar masses by assuming a one-to-one mapping that preserves the rank ordering between its host halo/subhalo property and its luminosity or stellar mass
(\citealt{kravtsov2004,vale2004,tasitsiomi2004,conroy2009,guo2010,wetzel2010,Neisten2011,watson2012,rodriguez2012,kravstov2013,mao2015,chavez2016}). 
In practice, the standard abundance-matching models assume a monotonic mapping between the stellar mass/luminosity of galaxies and some host-halo property, such as 
the maximum circular velocity the host halo $V_\mathrm{max}$ that traces the depth of the gravitational potential well of the halo. Furthermore, a scatter is assumed in this one-to-one relation between galaxy property and halo/subhalo property. With this framework, abundance-matching models have been successfully used in modeling a wide range of the 
statistical properties of galaxies such as two-point correlation function (\citealt{reddick2013,lehman2015,hod_vs_sham}) as well as the group statistics of galaxies (\citealt{sham_gmf}).

@@

In the $\mathtt{SMDP}$ simulation, as discussed in \citet{halodemographic}, the Rockstar algorithm can reliably resolve halos with $\geq 100$ particles which corresponds to $M_{\rm vir} \geq 9.6 \times 10^{9} \; h^{-1}M_{\odot}$. The advantage of using the $\mathtt{SMDP}$ simulation is that it satisfies both the size and resolution requirements of studying the galaxy--halo connection in a wide range of luminosity thresholds. Fainter galaxy samples reside in lower mass halos, and the more luminous galaxy samples considered in this investigation occupy higher comoving volumes. Furthermore, since we are studying the higher order halo occupation statistics, the concentration-dependence in particular, it is important to use a simulation that can resolve the internal structure of halos. In the context of Subhalo-Abundance matching modeling, accuracy of which depends on subhalo completeness especially in the low mass limit, the $\mathtt{SMDP}$ simulation has been used to model the faintest galaxy samples in the SDSS data (see \citet{hod_vs_sham}). The added advantage of using the $\mathtt{SMDP}$ simulation over some of the other industrial simulation boxes commonly used in the literature such as $\mathtt{Bolshoi}$ (\citealt{Klypin2011,smallmultidark}) simulation is its larger comoving volume. Larger volume makes this simulation more suitable for performing inference with $L_{\star}$ (corresponding to $M_{\rm r} \sim -20.44$, see \citealt{blanton2003}) and more luminous than $L_{\star}$ galaxy samples that occupy larger comoving volumes.

@@

For our standard HOD model, we assume the HOD parameterization from \citet{zheng07}. 
According to this model, a dark matter halo can host a central galaxy and some number of satellite galaxies. The occupation of the central galaxies follows a nearest-integer distribution, 
and the occupation of the satellite galaxies follows a Poisson distribution. The expected number of centrals and satellites as a function of the host halo mass of $M_{h}$ are given by the following equations 
\begin{eqnarray}
\langle N_{\rm cen}(M_{h}) \rangle &=& \frac{1}{2}\Big[1+\Big(\frac{\log M_{h} - \log M_{\rm min}}{\sigma_{\log \rm{M}}} \Big) \Big], \label{hod:central}\\ 
\langle N_{\rm sat}(M_{h}) \rangle &=& \Big( \frac{M_{h} - M_{\rm{0}}}{M_{\rm 1}} \Big)^{\alpha}. \label{hod:satellite}
\end{eqnarray}

For populating the halos with galaxies, we follow the procedure described in \citet{2016arXiv160701782H}, and \citet{decorated}. The central galaxies are assumed to be at the center of the host dark matter halos. We assume that the central galaxies are at rest with respect to the bulk motion of the halos and their velocities are given by the velocity of the center of mass of their host halo. Note that this assumption is shown to be violated in brighter than $L_{\star}$ galaxy samples (see \citealt{guo2015}). But since we are not considering the redshift space 2PCF multipoles in our study, we do not expect this velocity bias to impact our inference. We place the satellite galaxies within the virial radius of the halo following a Navarro-Frenk-White profile (hereafter NFW; \citealt{nfw}). This approach is different from other simulation-based halo occupation modeling techniques (see \citealt{hod_vs_sham,zheng_guo}) in that the positions of the satellites are not assigned to the dark matter particles in the $N$-body simulation. 
The concentration of the NFW profile is given by the empirical mass-concentration relation provided by \citet{nfw_c(M)}. The velocities of the satellite galaxies are given by two components. The first component is the velocity of the host halo. The second component is the velocity of the satellite galaxy with respect to the host halo which is computed following the solution to the NFW profile Jeans equations (\citealt{more2010}). We refer the readers to \citet{decorated} for a more comprehensive and detailed discussion of the forward modeling of the galaxy mock catalogs.

\subsubsection{Model with Assembly bias}\label{subsubsec:decorated}
Now let us provide a brief overview of HOD modeling with $\mathtt{Heaviside}$ $\mathtt{Assemblybias}$ (referred to as the decorated HOD) introduced in \citet{decorated}. At a fixed halo mass $M_{h}$, halos are split into two populations: population of halos with the 0.5-percentile of highest concentration, and population of halos with 0.5 percentile of lowest concentration. For simplicity, we call the first population ``type-1'' halos, and the second population ``type-2'' halos. In the decorated HOD model, the expected number of central and satellite galaxies at a fixed halo mass $M_{h}$ in the two populations are given by

@@

In this occupation model, the allowable ranges that quantities $\delta N_{c,i}$ and $\delta N_{s,i}$ can take are given by 
\begin{eqnarray}
-\langle N_{c} | M_{h}\rangle \leq \delta N_{c,i} \leq \langle N_{c} | M_{h}\rangle
 , \label{eq:cen-bounds} \\
-\langle N_{s} | M_{h}\rangle \leq \delta N_{s,i} \leq \langle N_{s} | M_{h}\rangle. \label{eq:sat-bounds}
\end{eqnarray}
Afterwards, the assembly bias parameter $\mathcal{A}$ is defined in the following way:

\begin{eqnarray}
\delta N_{\alpha , 1}(M_{h}) &=& |\mathcal{A_\alpha}| \delta N_{\alpha , 1}^{\rm max}(M_{h}) \; \; \rm{if} \; \mathcal{A_\alpha} > 0,  \label{positive_A} \\
\delta N_{\alpha , 1}(M_{h}) &=& |\mathcal{A_\alpha}| \delta N_{\alpha , 1}^{\rm min}(M_{h}) \; \; \rm{if} \; \mathcal{A_\alpha} < 0, \label{negative_A}
\end{eqnarray}
where the subscript $\alpha = c , s$ stands for the centrals and satellites respectively, and $\delta N_{\alpha , 1}^{\rm max}(M_{h})$, $\delta N_{\alpha , 1}^{\rm min}(M_{h})$ are given by Eqs. \ref{eq:cen-bounds} and \ref{eq:sat-bounds}.

@@

Once the halo catalogs are populated with galaxies, the real-space positions and velocities of all mock galaxies are obtained. The next step is applying a redshift-space distortion transformation by assuming plane-parallel approximation.
Our use of plane parallel approximation is justified because of the narrow redshift range of the SDSS main galaxy sample considered in this study.
If we assume that the $\hat{z}$ axis is the line-of-sight direction, then with the transformation $(X,Y,Z) \rightarrow (S_x,S_y,S_z) = (X , Y ,Z + v_{z}(1+z)/H(z))$
for each galaxy with the real space coordinates $(X,Y,Z)$, velocities $(v_x,v_y,v_z)$, and redshift $z$, we obtain the redshift-space coordinate of the produced mock galaxies. Here we assume $z \simeq 0$, and therefore transformation is given by $(X,Y,Z) \rightarrow (X,Y,Z+v_{z}/H_{0})$.

@@

As described in \citet{decorated} and \citet{2016arXiv160701782H}, this approach makes no appeal to the fitting functions used in the analytical calculation of the 2PCF. The accuracy of these fitting functions is limited (\citealt{tinker08,tinker10,watson13}). Our approach also does not face the known issues of the treatment of halo exclusion and scale-dependent bias that can lead to potential inaccuracies in halo occupation modeling (see \citealt{vdb13}).

The projected 2PCF $w_{p}(r_{p})$ can be computed by integrating the 3D redshift space 2PCF $\xi(r_{p} , \pi)$ along the line-of-sight (where $r_{\rm p}$ and $\pi$ denote the projected and line-of-sight separation of galaxy pairs respectively):
\beq
w_{p}(r_{p}) = 2 \int_{0}^{\pi_{max}}\xi(r_{p} , \pi)\; d\pi
\label{los}
\eeq
For our 2PCF calculations, we use the $w_{\rm p}$ measurement functionality of the fast and publicly available pair-counter code $\mathtt{CorrFunc}$ (\citealt{corrfunc} , available at \url{https://github.com/manodeep/Corrfunc}). To be consistent with the SDSS measurements described in Section \ref{sec:data}, $w_{\rm{p}}(r_{\rm{p}})$ is obtained by the line-of-sight integration to $\pi_{max}=40 \; h^{-1}\rm{Mpc}$. Note that $w_{p}(r_{p})$ is measured in units of $h^{-1}\rm{Mpc}$. To be consistent with \citet{guo2015}, we use the same binning (as specified in Section \ref{sec:data}) to measure $w_{\rm p}$. In addition to the projected 2PCF, we use the number density given by the number of mock galaxies divided by the comoving volume of the $\mathtt{SMDP}$ simulation.

@@

The measurements consist of the number density $n_{g}$ and the projected 2PCF $w_{p}(r_{p})$ made by \citet{guo2015} for the volume-limited sample of galaxies in NYU Value Added Galaxy Catalog (\citealt{Blanton2005}) constructed from the SDSS DR7 main galaxy sample (\citealt{abazajian2009}). In particular, eight volume-limited luminosity-threshold samples are constructed with maximum absolute luminosity in $r$-band of -18, 18.5, -19, -19.5, -20, -20.5, -21, and -21.5. Qualitatively, these samples are constructed in a similar way to those constructed in \citet{zehavi2011}. For detailed differences between the samples in \citet{guo2015} and \citet{zehavi2011}, we refer the reader to the Table 1 and Table 2 in those papers respectively.

The projected 2PCFs are measured in 12 logarithmic $r_{p}$ bins (in units of $h^{-1}\rm{Mpc}$) of width $\Delta \log(r_{\rm p}) = 0.2$, starting from $r_{\rm{p}} = 0.1 \; h^{-1}\rm{Mpc}$. For all luminosity threshold samples, the integration along the line-of-sight (\ref{los}) are performed to $\pi_{max}=40 \; h^{-1}\rm{Mpc}$.

The 2PCF measurement of each luminosity-threshold sample is accompanied by a covariance matrix constructed using 400 jackknife sub-samples of the data. The number density measurements are also accompanied by uncertainties measured using the jackknife method. Furthermore, the covariance between the number denisty and the projected 2PCF measurements are neglected. As \citet{norberg} shows, parameter estimation using jackknife covariance matrices is conservative as the jackknife method overestimates the errors in the observations.

The advantage of using these measurements is that the effects of fiber collision systematic errors on the two-point statistics are corrected for (with the method described in \citealt{guo2012}), and therefore, these measurements provide accurate small scale clustering measurements. The assembly bias parameters introduced in section \ref{sec:method} can have a 10-percent level impacts on galaxy clustering (\citealt{decorated}). Presence of assembly bias in the satellite population impacts the very small-scale clustering (\citealt{decorated}). Moreover as \citet{sunayama2016} demonstrates, the scale-dependence of the halo assembly bias has a pronounced bump in the 1-halo to 2-halo transition regime (1$\sim$2 $h^{-1}\rm{Mpc}$). This scales can be impacted by fiber collision systematics. Precise investigation of the possible impact of this signal on the galaxy clustering modeling requires accurate measurements of 2PCF on small scales. 
The method of \citet{guo2012} is able to recover the true $\wpp$ with  $\sim 6\%$ accuracy in small scales ($r_{\rm{p}} = 0.1 \; h^{-1}\rm{Mpc}$) and with $\sim 2.5\%$ at relatively large scales $r_{\rm{p}} \sim 30 \; h^{-1}\rm{Mpc}$.

Note that the comoving volume of the $N$-body simulation used in this investigation is 64 $\times 10^{6} \; h^{-3}\rm{Mpc}^{3}$ which is larger than the comoving volume of all the luminosity-threshold samples in the SDSS data considered in this study except the two most luminous samples. The comoving volumes of the $M_{\rm r}<-21, \; 21.5$ samples are 71.74 and 134.65 (in units of $10^{6} h^{-3}\rm{Mpc}^{3}$) respectively. Since we are not studying very large scale clustering ($r_{\rm p} \leq 25 \; h^{-1}\rm{Mpc}$), using a slightly smaller box for those samples is justified.

@@

In particular, findings of (\citealt{weschler2006,sunayama2016})
have demonstrated that for the halos with mass bellow the collapse mass ($M \leq M_{\rm col} \simeq 10^{12.5}\; M_{\odot} $) the large scale bias of high-$V_{\rm max}$ or high-$c$ halos at a fixed halo mass is larger than that of the low-$V_{\rm max}$ or low-$c$ halos. This signal reverses and weakens for the high mass halos ($M \geq M_{\rm col}$). Note that the halo concentration traces the maximum circular velocity $V_{\rm max}$ such that halos with higher $V_{max}$ have higher concentration and vice versa (see \citealt{prada2012}). For halos described by NFW profile, at a fixed halo mass, halos with higher values of concentration have higher values of $V_{\rm max}$.

@@

The luminosity dependent trend in the constraints on the central assembly bias for the six dimmest samples can be attributed to the fact that the halo concentration is highly correlated with the maximum circular velocity $V_{\rm max}$ which is a tracer of the potential well of dark matter halos (\citealt{prada2012}). In a dark matter halo described by an NFW profile, the depth of the gravitational potential well of dark matter halos can be directly measured by the maximum circular velocity $V_{\rm max}$ (\citealt{vmax_potential}). In particular, the magnitude of the potential well at the center of an NFW halo---where the central galaxy is assumed to reside---scales as $V_{\rm max}^{2}$:
\beq
\Phi(r=0) = -\Big(\frac{V_{\rm max}}{0.465}\Big)^{2},
\eeq
 where $\Phi(r=0)$ is the central potential of an NFW profile. Note that $V_{\rm max}$ is also the quantity often used in the abundance matching technique in which the luminosity of galaxies is monotonically matched to $V_{\rm max}$ (see for example \citealt{reddick2013, hod_vs_sham, halodemographic}). The trend between the constraint on $\acen$ and the luminosity threshold of the samples may suggest that at a \emph{fixed} \emph{halo} \emph{mass}, the central galaxies in the dimmest sample ($M_{\rm r}<$-18 , -18.5) tend to reside in dark matter halos with shallower gravitational well, and as we probe brighter galaxy samples ($M_{\rm max}<$-19 , -19.5, -20, -20.5), at a \emph{fixed} \emph{halo} \emph{mass}, the central galaxies have a tendency to reside in dark matter halos with deeper gravitational potential well.

@@

However, our results suggest that for all the 8 luminosity-threshold samples, the satellite assembly bias parameter is largely unconstrained and consistent with zero. we do not expect the galaxy clustering data to be a sufficient statistics for obtaining constraints on the satellite assembly bias. Group statistics probes the high mass end of the galaxy--halo connection and is sensitive to the parameters governing the satellite population (see \citealt{sham_gmf, 2016arXiv160701782H}), and therefore these measurements may shed light on investigating assembly bias in the satellite population.

It is important to note that the halo mass range in which the central assembly bias $\acen$ affects the central galaxy population is the mass range that satisfies the condition $0<\langle N_{\rm cen}|M \rangle<1$. As a result, larger scatter parameter $\sigmam$ increases the dynamical mass range in which assembly bias affects the galaxy clustering. Note that in the regimes for which we obtain tighter constraints on $\acen$, the best-estimate value of the scatter parameter $\sigmam$ appears to be higher in the model with assembly bias. This is also evident in Figure \ref{fig:posterior}. The tendency of the model with assembly bias to push $\sigmam$ to higher values can be attributed to the tendency of this model to increase the effective dynamical mass range of $\acen$.

As evident in Table \ref{tab:constraints}, in the HOD model with assembly bias, the constraints found on the scatter parameter are not tight. This is in keeping with the results of \citealt{guo2015} (which uses the same SDSS data) according to which, the scatter parameter remains largely unconstrained when only $n_{g}$ and $w_{p}$ are used as observables. Note that scatter is better constrained for the most luminous galaxy samples (this is attributed to the steep dependence of the halo bias and halo mass function on halo mass in the high mass end). But since these samples live in the most massive halos, we do not expect the tighter constraints on scatter to help us constrain the central assembly bias parameter. \citealt{guo2015} shows that by employing additional measurements such as the monopole ($\xi_{0}$), quadruple ($\xi_{2}$), hexadecapole ($\xi_{4}$), one can obtain tighter constraints on the scatter parameter. Tightening of constraints on the scatter parameters leads to reduction of uncertainty in the inferred central assembly bias parameter.
